The dependence of spiral disk morphology on the star formation-stellar mass relation

### 2014-08-12 mainsequence_morph.tex
Updated intro

Discuss (\kevin) seminal work of \citet{pen10a,pen12,pen14a,pen14} on gas regulator model and how mass/environment drive galaxy evolution.

>>>>

The fact that star-forming galaxies live on the SFMS is one of the key observations that has been driving the development of new descriptions of how galaxies evolve. \citet{pen10a,pen12} argue that galaxies grow in stellar mass during their life as star-forming galaxies on the main sequence before being quenched either by an external mechanism (environment or satellite quenching) or by an internal mechanism (mass quenching). This life on the main sequence is thus governed by the action of the regulator balancing gas in- and outflows \citet{lil13}, making it the central process in galaxy evolution.
